\newpage




\begin{thebibliography}{99}
\makeatletter
\renewcommand{\@biblabel}[1]{}
\makeatother
\bibitem{}


\makeatletter
\renewcommand{\@biblabel}[1]{[#1]}
\setcounter{enumiv}{0} \makeatother


\subsubsection{ \emph{Testi di
Algebra e Geometria}}



\bibitem{Abeasis}
Abeasis, S. : {\em Elementi di algebra lineare e geometria}, Zanichelli,  1993.

\bibitem{AxlerLinearAlgebra2015}
Axler, S., {\em Linear Algebra Done Right}, 3rd Ed., Springer, 2015.

\bibitem{BellmanIntroduction1997}
Bellman, R., {\em Introduction to Matrix Analysis}, 2nd Ed., SIAM, 1997.

\bibitem{DemmelApplied1997}
Demmel, J.W., {\em Applied Numerical Linear Algebra}, SIAM, 1997.

\bibitem{Dicuonzo}
Dicuonzo, V. : {\em Introduzione all'algebra lineare e alla geometria analitica}, Veschi,  1991.

\bibitem{friedberg2003linear}
Friedberg, S. H., Insel, A. J., \& Spence, L. E. :
\textit{Linear algebra} (4th ed.).
Pearson, (2003)

\bibitem{Gasparini}
Gasparini, I. C. : {\em Strutture algebriche e operatori lineari}, Eredi Virgilio Veschi,  1975.

\bibitem{GolubVanLoan2013}
Golub, G.H. and Van Loan, C.F., {\em Matrix Computations}, 4th Ed., Johns Hopkins University Press, 2013.

\bibitem{GriffithsMatrices2013}
Griffiths, D.F. and Higham, D.J., {\em Numerical Methods for Ordinary Differential Equations: Initial Value Problems}, Springer, 2013.

\bibitem{hoffman2018linear}
Hoffman, K., \& Kunze, R. : 
\textit{Linear algebra} (2nd ed.).
Pearson, (2018)

\bibitem{HornJohnson2012}
Horn, R.A. and Johnson, C.R., {\em Matrix Analysis}, 2nd Ed., Cambridge University Press, 2012.

\bibitem{KincaidNumericaAlgebra2009}
Kincaid, D. and Cheney, W., {\em Numerical Analysis: Mathematics of Scientific Computing}, 3rd Ed., American Mathematical Society, 2009.

\bibitem{LayLinearAlgebra2015}
Lay, D.C., Lay, S.R. and McDonald, J.J., {\em Linear Algebra and Its Applications}, 5th Ed., Pearson, 2015.

\bibitem{MeyerMatrix2000}
Meyer, C.D., {\em Matrix Analysis and Applied Linear Algebra}, SIAM, 2000.

\bibitem{strang2006linear}
Strang, G. :
\textit{Linear algebra and its applications} (4th ed.).
Thomson, Brooks/Cole, (2006)

\bibitem{StrangLinearAlgebra2016}
Strang, G., {\em Introduction to Linear Algebra}, 5th Ed., Wellesley-Cambridge Press, 2016.

\bibitem{TrefethenBauNumerical1997}
Trefethen, L.N. and Bau III, D., {\em Numerical Linear Algebra}, SIAM, 1997.

\bibitem{Vaccaro}
Vaccaro, G., Carfagna, A., Piccolella, L. {\em Lezioni di geometria e  algebra lineare}, Zanichelli,  1995.

\bibitem{VargaMatrixIterative2009}
Varga, R.S., {\em Matrix Iterative Analysis}, 2nd Ed., Springer, 2009.




\vspace{0.6 cm}
\subsubsection{\emph{Argomenti di Analisi vettoriale e tensoriale}}


\bibitem{Borisenko}
A.I. Borisenko, I.E. Tarapov {\em Vector and tensor analysis with
	applications}, Dover Publications, Inc., New York 1979.


\bibitem{bramanti}
M. Bramanti, C.D. Pagani, S. Salsa \emph{Matematica, calcolo
	infinitesimale e algebra lineare}, Zanichelli, 2000.


\bibitem{Pagani}
C.D. Pagani, S. Salsa \emph{Analisi matematica} vol. 1 e 2, Masson, 1998.


\bibitem{Ghizzetti1}
A. Ghizzetti, F. Rosati {\em Analisi matematica}, vol. I e II,
MASSON editoriale Veschi, 1992.





\vspace{0.6 cm}
\subsubsection{\emph{Argomenti di statica e meccanica delle strutture}}



\bibitem{Angeles}
Angeles, J. and Kecskemethy, A., {\em Kinematics and Dynamics of Multi-Body Systems}, Springer Vienna, 2014.

\bibitem{DB}
Bernardini, D. \emph{Statica - Un'introduzione alla meccanica delle strutture}, CittàStudi Edizioni, 2009. 

\bibitem{Bower2009}
Bower, A.F., {\em Applied Mechanics of Solids}, CRC Press, 2009.

\bibitem{Carpinteri1}
Carpinteri, A. \emph{Structural Mechanics - A unified approach}, E \& FN SPON, 1997.

\bibitem{Carpinteri2}
Carpinteri, A. \emph{Structural Mechanics Fundamentals}, CRC Press., 2014.

\bibitem{Carpinteri2002}
Carpinteri, A., {\em Structural Mechanics: A Unified Approach}, CRC Press, 2002.

\bibitem{CeradiniSCR}
Ceradini, G. : {\em Cinematica e statica dei sistemi rigidi}, in Scienza
delle Costruzioni a cura di G. Ceradini, Vol. 1, ESA Roma, 1991.

\bibitem{Corradi1A}
Comi, C., Corradi Dell'Acqua, L. : {\em Introduzione alla meccanica
	strutturale}, McGraw-Hill, 2003.

\bibitem{DenHartog2}
Den Hartog, J. P. \emph{Mechanics}, Dover Pubblications, Inc., New
York, 1961.

\bibitem{Emri}
Emri, I., Voloshin, A. {\em Statics - Learning from Engineering Examples}, Springer, 2016.

\bibitem{GereGoodno2012}
Gere, J.M. and Goodno, B.J., {\em Mechanics of Materials}, 8th Ed., Cengage Learning, 2012.

\bibitem{Govindjee2012}
Govindjee, S., {\em Engineering Mechanics of Deformable Solids: A Presentation with Exercises}, Oxford University Press, 2012.

\bibitem{GBGN}
Guagenti, E., Buccino, F., Garavaglia, E., Novati, G. : \emph{Statica,
	fondamenti di meccanica strutturale}, McGraw-Hill, seconda edizione,
2004.

\bibitem{Hahn}
Hahn, H., {\em Rigid Body Dynamics of Mechanisms: 1 Theoretical Basis}, Springer Berlin Heidelberg, 2013.

\bibitem{Hughes}
Hughes, J. H., Martin, K. F., {\em Basic Engineering Mechanics}, Macmillan Education UK, 1977.

\bibitem{HulseCain2000}
Hulse, R. and Cain, J., {\em Structural Mechanics: Worked Examples}, Palgrave, 2000.

\bibitem{Johnson2000}
Johnson, D., {\em Advanced Structural Mechanics}, Thomas Telford Ltd., 2000.

\bibitem{Krenk}
Krenk, S., Høgsberg, J., {\em Statics and Mechanics of Structures}, Springer 2012. 

\bibitem{LP}
Luongo, A., Paolone, A. : {\em Meccanica delle strutture: sistemi
	rigidi ad elasticit\`{a} concentrata}, CEA, seconda edizione,
2004.

\bibitem{Mau}
Mau, S. T. {\em Introduction to Structural Analysis - Displacement and Force Methods}, CRC Press, Taylor \& Francis Group, 2012.

\bibitem{McGuire}
McGuire, Gallagher, Ziemian, {\em Matrix structural analysis}, Ziemian 2014.

\bibitem{Paz}
Paz, Leigh, {\em Integrated matrix analysis of structures}, Kluwer academic publisher 2001.

\bibitem{Podio2}
Podio Guidugli, P. : {\em Lezioni di statica}, Aracne editrice, 2014.

\bibitem{Ranzi}
Ranzi, G., Gilbert, R.I. {\em Structural Analysis - Principle, Methods and Modelling}, CRC Press, Taylor \& Francis Group, 2015.

\bibitem{Smith2001}
Smith, P., {\em Introduction to Structural Mechanics}, Palgrave, 2001.

\bibitem{Mete}
Sozen, M. A., Ichinose, T. {\em Undesrtanding Structures - An introduction to Structural Analysis}, CRC Press, Taylor \& Francis Group, 2009.

\bibitem{Taliercio}
Taliercio, Perego, {\em Fundamentals of Structural Mechanics}, Esculapio 2023.

\bibitem{UguralFenster2003}
Ugural, A.C. and Fenster, S.K., {\em Advanced Strength and Applied Elasticity}, 4th Ed., Prentice Hall, 2003.

\bibitem{Williams2009}
Williams Jr., J. H., {\em Structural Mechanics: Fundamentals and Applications}, CRC Press, 2009.

\bibitem{WunderlichPilkey2002}
Wunderlich, W. and Pilkey, W. D., {\em Principles of Structural Analysis: Static and Dynamic Loads}, CRC Press, 2002.




\vspace{0.6 cm}
\subsubsection{\emph{Metodi integrali ed energetici }}



\bibitem{Capecchi2012}
Capecchi, D., {\em History of Virtual Work Laws: A History of Mechanics Prospective}, Birkh$\ddot{a}$user, 2012.

\bibitem{Koiter1969}
Koiter, W.T., "Virtual work and power in applied mechanics", {\em Journal of Applied Mechanics}, 1969.

\bibitem{Reddy2017}
Reddy, J.N., {\em Energy Principles and Variational Methods in Applied Mechanics}, 3rd Ed., Wiley, 2017.

\bibitem{Salencon}
Salencon, J., {\em Virtual Work Approach to Mechanical Modeling}, John Wiley \& Sons, 2018.

\bibitem{SzeLiuLo2019}
Sze, K.Y., Liu, X.H. and Lo, S.H., {\em Virtual Work and Shape Change in Solid Mechanics}, Springer, 2019.

\bibitem{Valipour2015}
Valipour, H.R. et al., "The principle of virtual work in structural analysis", {\em Computers \& Structures}, 2015.



\vspace{0.6 cm}
\subsubsection{\emph{Stabilità e biforcazione dell'equilibrio }}

\bibitem{BazantCedolin2010}
Bazant, Z.P. and Cedolin, L., {\em Stability of Structures: Elastic, Inelastic, Fracture and Damage Theories}, World Scientific, 2010.

\bibitem{ChenLui2005}
Chen, G. and Lui, S.H., {\em Stability of Infinite Dimensional Dynamical Systems}, Springer, 2005.

\bibitem{GolubitskySteward2012}
Golubitsky, M. and Stewart, I., {\em Singularities and Groups in Bifurcation Theory: Volume II}, Springer, 2012.

\bibitem{GuoLuo2015}
Guo, Y. and Luo, A.C.J., {\em Bifurcation Theory and Applications}, World Scientific, 2015.

\bibitem{IkedaMurota2002}
Ikeda, K. and Murota, K., {\em Imperfect Bifurcation in Structures and Materials: Engineering Use of Group-Theoretic Bifurcation Theory}, Springer, 2002.

\bibitem{KellerBifurcation1987}
Keller, H.B., "Lectures on Numerical Methods in Bifurcation Problems", {\em Tata Institute of Fundamental Research}, 1987.

\bibitem{KireenkoNakashima2017}
Kireenko, O.F. and Nakashima, M., {\em Structural Stability: Theory and Implementation}, CRC Press, 2017.

\bibitem{KrauskopfOsingaGalan2007}
Krauskopf, B., Osinga, H.M. and Galan-Vioque, J., {\em Numerical Continuation Methods for Dynamical Systems}, Springer, 2007.

\bibitem{NayfehBalachandran1995}
Nayfeh, A.H. and Balachandran, B., {\em Applied Nonlinear Dynamics: Analytical, Computational, and Experimental Methods}, Wiley, 1995.

\bibitem{SeydellPractical2010}
Seydel, R., {\em Practical Bifurcation and Stability Analysis}, 3rd Ed., Springer, 2010.

\bibitem{ThompsonHunt1984}
Thompson, J.M.T. and Hunt, G.W., {\em Elastic Instability Phenomena}, Wiley, 1984.





\vspace{0.6 cm}
\subsubsection{\emph{Plasticità}}


\bibitem{BoresiElasticity2000}
Boresi, A.P. and Schmidt, R.J., {\em Advanced Mechanics of Materials}, 6th Ed., Wiley, 2000.

\bibitem{ChakrabartyTheory2006}
Chakrabarty, J., {\em Theory of Plasticity}, 3rd Ed., Butterworth-Heinemann, 2006.

\bibitem{DrukerPlasticity1951}
Drucker, D.C., "A more fundamental approach to plastic stress-strain relations", {\em Proceedings of the First U.S. National Congress of Applied Mechanics}, 1951.

\bibitem{HillMathematical1998}
Hill, R., {\em The Mathematical Theory of Plasticity}, Oxford University Press, 1998.

\bibitem{KachanovFundamentals2004}
Kachanov, L.M., {\em Fundamentals of the Theory of Plasticity}, Dover Publications, 2004.

\bibitem{KhanHuang1995}
Khan, A.S. and Huang, S., {\em Continuum Theory of Plasticity}, Wiley, 1995.

\bibitem{KriegPlasticity2017}
Krieg, R.D. and Krieg, D.B., {\em Plasticity: Theory and Applications}, Wiley, 2017.

\bibitem{LublinerPlasticity2008}
Lubliner, J., {\em Plasticity Theory}, Dover Publications, 2008.

\bibitem{NeedlemanComputational2000}
Needleman, A., "Computational plasticity: Accomplishments and challenges", {\em International Journal of Plasticity}, Vol. 16, No. 5, 2000.

\bibitem{RicePlasticity1971}
Rice, J.R., "Inelastic constitutive relations for solids: An internal-variable theory and its application to metal plasticity", {\em Journal of the Mechanics and Physics of Solids}, Vol. 19, No. 6, 1971.

\bibitem{SaeediBodner2008}
Saeedi, N. and Bodner, S.R., {\em Plasticity: Modeling \& Computation}, Springer, 2008.

\bibitem{SikoraPlasticity2020}
Sikora, L., {\em Plasticity: Theory and Engineering Applications}, Elsevier, 2020.

\bibitem{SimoHughes1998}
Simo, J.C. and Hughes, T.J.R., {\em Computational Inelasticity}, Springer, 1998.

\bibitem{YuMechanics2006}
Yu, M.H., {\em Generalized Plasticity}, Springer, 2006.


\end{thebibliography}
